Constructing Sailing Match Race Schedules: Round Robin Pairing Lists

### 2015-03-24 paper.tex
cdot for multiply

The first thing we model is a skipper. A skipper $\sigma$ has a temporal view
of his schedule in the array of constrained integer variables $\timeSlot[0]$ to
$\timeSlot[{t-1}]$ (\eqref{var:timeSlot} below), and a state view in the array
of constraint integer variables $\state[0]$ to $\state[{f-1}]$
(\eqref{var:state} below), i.e.\ $\state[i]$ is the state of this skipper in
flight $i$ and corresponds to timeslots $\timeSlot[{i*m}]$ to
$\timeSlot[{m(i+1)-1}]$.

>>>>

The first thing we model is a skipper. A skipper $\sigma$ has a temporal view
of his schedule in the array of constrained integer variables $\timeSlot[0]$ to
$\timeSlot[{t-1}]$ (\eqref{var:timeSlot} below), and a state view in the array
of constraint integer variables $\state[0]$ to $\state[{f-1}]$
(\eqref{var:state} below), i.e.\ $\state[i]$ is the state of this skipper in
flight $i$ and corresponds to timeslots $\timeSlot[{i \cdot m}]$ to
$\timeSlot[{m(i+1)-1}]$.
